---
title: "R Notebook"
output: html_notebook
---

General goal: this script will parse over 20 million lines of weather data stored locally on Carey's computer. Output aims at aggregating historical weather data for target dates for target county centroids 


Manage packages
```{r}
pacman::p_load(tidyverse)
```

Get a list of target dates.
```{r}
date_target <- seq.Date(as.Date("2000-01-01"),
                         as.Date("2010-12-31"),
                         b = "week")

week <- seq(1:length(date_target))
weekz <- data.frame(week, date_target) 

rm(week)
```

Get a list of counties with their identifies.
```{r}

working_d <- getwd()
working_d <- str_sub(working_d, end = -7)
yuio <- paste0(working_d, "data/counties_shp2.rds")

dfc <- read_rds(yuio)                        ##use the geoid in this to reference counties

###remove counties with API failures
api_failures <- c(278, 379, 383, 572, 1024, 1853, 2923)




weather_dir <- "C:/Users/Carey Suehs/Documents/weather/"
```

Initiate a dataframe by aggregating the first target date. Create a loop to parse the weather data in the first county and bind it to the aggregated data.
```{r}



for (i in 279:281){

gid <- dfc$GEOID[i]
name_of_file <- paste0("GEOID_", gid, ".csv")
name_of_path <- paste0(weather_dir, name_of_file)

df <- read.csv(name_of_path)
df$Date.time <- as.character(df$Date.time)
df$Date.time <- as.Date(df$Date.time, format = "%m/%d/%Y")

####### get means and slopes for the three weeks preceding target dates starting at target date '4'.

j <- 4
tdate <- weekz$date_target[j]
start_date <- tdate-21
date_range <- seq.Date(start_date, tdate, b = "day")

temp <- df[df$Date.time %in% date_range,]

aggregated_weather2 <- temp %>% 
  summarise(av_temp_hi = mean(Maximum.Temperature),
            av_temp_lo <- mean(Minimum.Temperature),
            av_temp_mean <- mean(Temperature),
            av_precip <- mean(Precipitation),
            av_wind_speed <- mean(Wind.Speed),
            av_cloud_cover <- mean(Cloud.Cover),
            av_humidity <- mean(Relative.Humidity))

colnames(aggregated_weather2) <- c("av_temp_hi",
                                  "av_temp_lo",
                                  "av_temp_mean",
                                  "av_precip",
                                  "av_wind_speed",
                                  "av_cloud_cover",
                                  "av_humidity")
aggregated_weather2$week <- weekz$week[j]
aggregated_weather2$date_target <- weekz$date_target[j]
aggregated_weather2$geoid <- gid                   


for (j in 5:length(weekz$week)) {
  tdate <- weekz$date_target[j]
  start_date <- tdate-21
  date_range <- seq.Date(start_date, tdate, b = "day")

  temp <- df[df$Date.time %in% date_range,]

  new_row <- temp %>% 
  summarise(av_temp_hi = mean(Maximum.Temperature),
            av_temp_lo <- mean(Minimum.Temperature),
            av_temp_mean <- mean(Temperature),
            av_precip <- mean(Precipitation),
            av_wind_speed <- mean(Wind.Speed),
            av_cloud_cover <- mean(Cloud.Cover),
            av_humidity <- mean(Relative.Humidity))

  colnames(new_row) <- c("av_temp_hi",
                                  "av_temp_lo",
                                  "av_temp_mean",
                                  "av_precip",
                                  "av_wind_speed",
                                  "av_cloud_cover",
                                  "av_humidity")
  new_row$week <- weekz$week[j]
  new_row$date_target <- weekz$date_target[j]
  new_row$geoid <- gid
  aggregated_weather2 <- rbind(aggregated_weather2, new_row)
  name_of_new_file <- paste0("agg_", name_of_file)
  name_of_new_path <- paste0("C:/Users/Carey Suehs/Documents/weather_aggregated/", name_of_new_file)
  write.csv(aggregated_weather2, name_of_new_path)
  
}

print(i)
}
```


```{r}



for (i in 380:382){

gid <- dfc$GEOID[i]
name_of_file <- paste0("GEOID_", gid, ".csv")
name_of_path <- paste0(weather_dir, name_of_file)

df <- read.csv(name_of_path)
df$Date.time <- as.character(df$Date.time)
df$Date.time <- as.Date(df$Date.time, format = "%m/%d/%Y")

####### get means and slopes for the three weeks preceding target dates starting at target date '4'.

j <- 4
tdate <- weekz$date_target[j]
start_date <- tdate-21
date_range <- seq.Date(start_date, tdate, b = "day")

temp <- df[df$Date.time %in% date_range,]

aggregated_weather2 <- temp %>% 
  summarise(av_temp_hi = mean(Maximum.Temperature),
            av_temp_lo <- mean(Minimum.Temperature),
            av_temp_mean <- mean(Temperature),
            av_precip <- mean(Precipitation),
            av_wind_speed <- mean(Wind.Speed),
            av_cloud_cover <- mean(Cloud.Cover),
            av_humidity <- mean(Relative.Humidity))

colnames(aggregated_weather2) <- c("av_temp_hi",
                                  "av_temp_lo",
                                  "av_temp_mean",
                                  "av_precip",
                                  "av_wind_speed",
                                  "av_cloud_cover",
                                  "av_humidity")
aggregated_weather2$week <- weekz$week[j]
aggregated_weather2$date_target <- weekz$date_target[j]
aggregated_weather2$geoid <- gid                   


for (j in 5:length(weekz$week)) {
  tdate <- weekz$date_target[j]
  start_date <- tdate-21
  date_range <- seq.Date(start_date, tdate, b = "day")

  temp <- df[df$Date.time %in% date_range,]

  new_row <- temp %>% 
  summarise(av_temp_hi = mean(Maximum.Temperature),
            av_temp_lo <- mean(Minimum.Temperature),
            av_temp_mean <- mean(Temperature),
            av_precip <- mean(Precipitation),
            av_wind_speed <- mean(Wind.Speed),
            av_cloud_cover <- mean(Cloud.Cover),
            av_humidity <- mean(Relative.Humidity))

  colnames(new_row) <- c("av_temp_hi",
                                  "av_temp_lo",
                                  "av_temp_mean",
                                  "av_precip",
                                  "av_wind_speed",
                                  "av_cloud_cover",
                                  "av_humidity")
  new_row$week <- weekz$week[j]
  new_row$date_target <- weekz$date_target[j]
  new_row$geoid <- gid
  aggregated_weather2 <- rbind(aggregated_weather2, new_row)
  name_of_new_file <- paste0("agg_", name_of_file)
  name_of_new_path <- paste0("C:/Users/Carey Suehs/Documents/weather_aggregated/", name_of_new_file)
  write.csv(aggregated_weather2, name_of_new_path)
  
}

print(i)
}
```












