---
title: "R Notebook"
output: html_notebook
---

Manage packages.
```{r}
pacman::p_load(tidyverse, glmnet, gbm, rpart,
               randomForest, caret, kernlab, pROC)
```

Get data.
```{r}

train_weather <- read_csv("C:/Users/Carey Suehs/Documents/GitHub/Wild_Fires/data/train_aggregated_weather_1_853.csv") %>% select(-1,-2) %>%
  mutate(annee=str_sub(date_target,1,4),
         geoid = ifelse(nchar(geoid)<5,paste0("0",geoid),geoid))

data_train <- read_csv("C:/Users/Carey Suehs/Documents/GitHub/Wild_Fires/data/semaine_train.csv") 
  
magic <- left_join(data_train,train_weather %>% select(-week,-annee),
                   by = c("county"="geoid",
                          "date_semaine"="date_target"))
florida <- magic %>% 
  filter(state == 12)

rm(data_train, train_weather)
```

Create a dataframe with only those variables that will be entering the model
```{r}

nokeep <- c("county", 
            "state", 
            "date_semaine",
            "annee",
            "semaine",
            "nb",
            "area_burned",
            "Debris.Burning",
            "Arson",
            "Children",
            "Campfire" ,
            "Smoking" ,
            "Equipment.Use",
            "Lightning",
            "Miscellaneous",
            "Powerline",
            "Railroad" ,
            "Fireworks",
            "Missing.Undefined" ,
            "Structure",
            "nb_feux_voisins",
            "X12_Perennial_ice_snow",
            "X0_0")

dfmm <- florida[complete.cases(florida),!names(florida) %in% nokeep]    #### complete cases!!!

dfmm$FIRE <- as.numeric(dfmm$FIRE)

colnames(dfmm)[1] <- "Y"    #Make sure the dependent variable is in position '1' and rename as 'Y'.

rm(magic)

#df <- sample_n(dfmm,2000)   ##################reset this will full data after attenmpting small set
df <- dfmm
```





```{r}

```






Set up the independent and dependent variables
```{r}
xxx <- model.matrix(Y ~ ., df)
yyy <- df$Y
```

Set up the cross validation block structure.
```{r}
nbloc <- 5
bloc <- rep(1:nbloc, length=nrow(df))
set.seed(1234)
bloc <- sample(bloc)
length(bloc)
```

Set up results frame.
```{r}
res <- data.frame(yyy, 
                  logistic=0, 
                  step=0, 
                  glmridge=0, 
                  glmlasso=0,
                  glmelastic=0,
                  boosted200=0,
                  boosted500=0,
                  cart=0,
                  randomforest200=0,
                  randomforest500=0,
                  svm=0)
```



Make a loop that places predicted values for the selected models into the results frame.
```{r}
for (i in 1:nbloc){
  dfA <- df[bloc != i,]
  XXA <- xxx[bloc != i,]
  YYA <- yyy[bloc != i]
  dfT <- df[bloc == i,]
  XXT <- xxx[bloc == i,]
  ###################################################################
  mod_log <- glm(Y~., data=dfA, family = "binomial")
  res[bloc==i, "logistic"] <- predict(mod_log,dfT, type = "response")
  print(paste0("logistic_",i))
  #####
  mod_step <- step(mod_log, trace=0, direction = "both")
  res[bloc==i, "step"] <- predict(mod_step, dfT, type = "response")
  print(paste0("step_",i))
  #####
  mod_ridge <- cv.glmnet(x = XXA, y = YYA, alpha=0, family = "binomial")
  res[bloc==i, "glmridge"] <- as.vector(predict(mod_ridge, newx=XXT, type="response"))
  print(paste0("ridge_",i))
  #####
  mod_lasso <- cv.glmnet(x = XXA, y = YYA, alpha=1, family = "binomial")
  res[bloc==i, "glmlasso"] <- as.vector(predict(mod_lasso, newx=XXT, type="response"))
  print(paste0("lasso_",i))
  #####
  mod_elastic <- cv.glmnet(x = XXA, y = YYA, alpha=0.5, family = "binomial")
  res[bloc==i, "glmelastic"] <- as.vector(predict(mod_elastic, newx=XXT, type="response"))
  print(paste0("elastic_",i))
  #####
  #mod_boost200 <- gbm(formula = Y~., data = dfA, distribution = "adaboost",
            #n.trees = 200, interaction.depth = 2, shrinkage = 0.02) 
  #res[bloc == i, "boosted200"] <- as.vector(predict(mod_boost200, newdata = dfT, type="response"))
  #print(paste0("boost200_",i))
  #####
  mod_boost500 <- gbm(formula = Y~., data = dfA, distribution = "adaboost",
            n.trees = 500, interaction.depth = 2, shrinkage = 0.02) 
  res[bloc == i, "boosted500"] <- as.vector(predict(mod_boost500, newdata = dfT, type="response"))
  print(paste0("boost500_",i))
  #####
  mod_cart <- rpart(formula = Y~., data = dfA)
  res[bloc == i, "cart"] <- predict(mod_cart, dfT)
  print(paste0("cart_",i))
  #####
  #mod_randomforest200 <- randomForest(formula = Y~., data = dfA, ntree=200)
  #res[bloc == i, "randomforest200"] <- predict(mod_randomforest200, newdata = dfT, ytype = "prob")
  #print(paste0("randomforest200_",i))
  #####
  mod_randomforest500 <- randomForest(formula = Y~., data = dfA, ntree=500)
  res[bloc == i, "randomforest500"] <- predict(mod_randomforest500, newdata = dfT, ytype = "prob")
  print(paste0("randomforest500_",i))
  #####
  #trctrl <- trainControl(method = "boot")
  #dfAA <- dfA
  #dfAA$Y <- as.factor(dfAA$Y)
  #dfTT <- dfT
  #dfTT$Y <- as.factor(dfTT$Y)
  #mod_svm <- train(Y ~., data = dfAA, method = "svmLinear",
                # trControl=trctrl,
                 #preProcess = c("center", "scale"),
                 #tuneLength = 10)
  #res[bloc == i, "svm"] <- predict(mod_svm, newdata = dfTT)
  #print(paste0("svm_",i))
  #####
  #####
  #####
  #####
  #####
  #####
  print(i)
}

res$svm <- ifelse(res$svm==1, 0, 1)
```



Creat ROC objects from the pROC package.
```{r}

r1 <- roc(res$yyy, res$logistic)
r2 <- roc(res$yyy, res$step)
r3 <- roc(res$yyy, res$glmridge)
r4 <- roc(res$yyy, res$glmlasso)
r5 <- roc(res$yyy, res$glmelastic)
#r6 <- roc(res$yyy, res$boosted200)
r7 <- roc(res$yyy, res$boosted500)
r8 <- roc(res$yyy, res$cart)
#r9 <- roc(res$yyy, res$randomforest200)
r10 <- roc(res$yyy, res$randomforest500)





```





```{r}
modz <- c("logistic",
          "step",
          "ridge",
          "lasso",
          "elastic",
          #"boost200",
          "boost500",
          "cart",
          #"randomforest200",
          "randomforest500")
auc <- c(auc(r1), 
         auc(r2),
         auc(r3),
         auc(r4),
         auc(r5),
         #auc(r6),
         auc(r7),
         auc(r8),
         #auc(r9),
         auc(r10))

rm(thresh)
thresh <- rbind (coords(r1, "best", best.method = "c"),
                 coords(r2, "best", best.method = "c"),
                 coords(r3, "best", best.method = "c"),
                 coords(r4, "best", best.method = "c"),
                 coords(r5, "best", best.method = "c"),
                 #coords(r6, "best", best.method = "c"),
                 coords(r7, "best", best.method = "c"),
                 coords(r8, "best", best.method = "c"),
                 #coords(r9, "best", best.method = "c"),
                 coords(r10, "best", best.method = "c"))

res_auc <- data.frame(modz,auc,thresh)
res_auc
res_auc$tot <- res_auc$specificity+res_auc$sensitivity

res_auc <- res_auc[order(res_auc$tot),]
res_auc
thresh
```


Create a function that returns the error of classification.
```{r}
eval_prev_classif <- function(prev_proba,
                              real,
                              threshi){
  prev <- (prev_proba > threshi)*1
  
  cm <- table(real,prev)
  cm_norm <- round(100*cm/sum(cm),digits=1)
  
  
  tp <- cm[2,2]
  fp <- cm[1,2]
  tn <- cm[1,1]
  fn <- cm[2,1]

  error <- (fp+fn)/(tp+tn+fp+fn)
  
  #print(cm)
  #print(cm_norm)
  #print(paste("Classification error : ",round(error,digits=3),sep=""))
  
  round(error,digits=3)*100
}
```



```{r}
res_auc$classif_error <- NA
res_auc$classif_error[res_auc$modz == "cart"] <- eval_prev_classif(res$cart, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "cart"])
res_auc$classif_error[res_auc$modz == "ridge"] <- eval_prev_classif(res$glmridge, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "ridge"])
res_auc$classif_error[res_auc$modz == "logistic"] <- eval_prev_classif(res$logistic, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "logistic"])
res_auc$classif_error[res_auc$modz == "step"] <- eval_prev_classif(res$step, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "step"])
res_auc$classif_error[res_auc$modz == "elastic"] <- eval_prev_classif(res$glmelastic, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "elastic"])
res_auc$classif_error[res_auc$modz == "lasso"] <- eval_prev_classif(res$glmlasso, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "lasso"])
#res_auc$classif_error[res_auc$modz == "boost200"] <- eval_prev_classif(res$boosted200, 
                                                                   #res$yyy, 
                                                                   #res_auc$threshold[res_auc$modz == #"boost200"])
res_auc$classif_error[res_auc$modz == "boost500"] <- eval_prev_classif(res$boosted500, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "boost500"])
#res_auc$classif_error[res_auc$modz == "randomforest200"] <- eval_prev_classif(res$randomforest200, 
                                                                   #res$yyy, 
                                                                   #res_auc$threshold[res_auc$modz == #"randomforest200"])
res_auc$classif_error[res_auc$modz == "randomforest500"] <- eval_prev_classif(res$randomforest500, 
                                                                   res$yyy, 
                                                                   res_auc$threshold[res_auc$modz == "randomforest500"])

res_auc
```


```{r}
pdf(file = "florida_roc.pdf")

plot.roc(res$yyy, 
                  res$logistic, 
                  main="Confidence intervals", 
                  percent=TRUE, 
                  ci=TRUE, # compute AUC (of AUC by default) 
                  of="thresholds",
                  thresholds="best",
                  print.thres="best",
                  print.auc=TRUE,# print the AUC (will contain the CI)
                  legacy.axes = F,
         xlim=c(100,0)) 

dev.off()
```


```{r}
ggroc(r1, legacy.axes = T) +
geom_abline(slope = 1 ,intercept = 0) + # add identity line
theme(
panel.background = element_blank(), 
axis.title.x = element_text(size =18, face = 'bold'),
axis.title.y = element_text(size =18, face = 'bold'),
panel.border = element_rect(size = 2, fill = NA), 
axis.text.x = element_text(size = 14, face ='bold'),
axis.text.y = element_text(size = 14, face ='bold')) +
xlab('100% - Specificity') +
ylab('100% - Sensitivity') +
scale_x_continuous(breaks = seq(0,1,0.25), labels = seq(0,1,0.25) * 100) + 
scale_y_continuous(breaks = seq(0,1,0.25), labels = seq(0,1,0.25) * 100)
```



Get the external test data.
```{r}
test_weather <- read_csv("C:/Users/Carey Suehs/Documents/GitHub/Wild_Fires/data/test_aggregated_weather_1_853.csv") %>% select(-1,-2) %>%
  mutate(annee=str_sub(date_target,1,4),
         geoid = ifelse(nchar(geoid)<5,paste0("0",geoid),geoid))

data_test <- read_csv("C:/Users/Carey Suehs/Documents/GitHub/Wild_Fires/data/semaine_test.csv") 

magic_test <- left_join(data_test,test_weather %>% select(-week,-annee),
                        by = c("county"="geoid",
                               "date_semaine"="date_target"))

test_florida <- magic_test %>% 
  filter(state == 12)
  
  

#df_test <- test_florida[complete.cases(test_florida),!names(test_florida) %in% nokeep]    #### #complete cases!!!

df_test <- test_florida[,!names(test_florida) %in% nokeep]
df_test$FIRE <- as.numeric(df_test$FIRE)

colnames(df_test)[1] <- "Y"    #Make sure the dependent variable is in position '1' and rename as#Y'.


```

```{r}
df_test$pred <- predict(mod_randomforest500, newdata = df_test, ytype = "prob")
```


```{r}
r_external_val <- roc(df_test$Y, df_test$pred, na.rm = T)
auc(r_external_val)
coords(r_external_val, "best", best.method = "c")
```


```{r}
plot.roc(df_test$Y, 
                  df_test$pred, 
                  main="Confidence intervals", 
                  percent=TRUE, 
                  ci=TRUE, # compute AUC (of AUC by default) 
                  of="thresholds",
                  thresholds="best",
                  print.thres="best",
                  print.auc=TRUE,# print the AUC (will contain the CI)
                  legacy.axes = F,
         xlim=c(100,0)) 
```


```{r}
test_florida$pred <- df_test$pred


write.csv(test_florida, "C:/Users/Carey Suehs/Documents/GitHub/Wild_Fires/models/florida_pred.csv")
```

```{r}
pdf("florida_roc_external.pdf")
plot.roc(df_test$Y, 
                  df_test$pred, 
                  main="Confidence intervals", 
                  percent=TRUE, 
                  ci=TRUE, # compute AUC (of AUC by default) 
                  of="thresholds",
                  thresholds="best",
                  print.thres="best",
                  print.auc=TRUE,# print the AUC (will contain the CI)
                  legacy.axes = F,
         xlim=c(100,0)) 
dev.off()
```



